---
title: "p8105_hw6_hw2850"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

###Problem 2
```{r}
#read data
homicide = read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names()
```

```{r}
homicide_tidy = homicide %>% 
  mutate(
    city_state = str_c(city, ", " ,state), #create city_state variable
    disposition = if_else(disposition %in% "Closed by arrest", 1, 0)
    ) %>% #make disposition a binary variable
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"),
         victim_race %in% c("White", "Black")) %>% #Only select white & black
  mutate(victim_age = as.numeric(victim_age), #make age numeric
         victim_race = fct_relevel(victim_race, "White"),
         disposition = as.numeric(disposition)) %>% 
  select(!c(city, state))
```

```{r}
Baltimore = homicide_tidy %>% 
  filter(city_state == "Baltimore, MD") #get Baltimore data

Baltimore_fit = Baltimore %>% 
  glm(disposition ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) #run glm

Baltimore_results = Baltimore_fit %>% 
  broom::tidy(conf.int = T) %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value, conf.low, conf.high) 
```

```{r}
homicide_nest = homicide_tidy %>% 
  select(city_state, victim_race, victim_age, victim_sex, disposition) %>%
  nest(data = -city_state) %>% #nest data and run glm on each city
  mutate(models = map(data, ~glm(disposition ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
         results = map(models, ~broom::tidy(x = .x, conf.int = T))) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(term %in% "victim_sexMale") %>% #only need sex coefficients
  mutate(OR = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high))
```

```{r}
homicide_plot = homicide_nest %>% 
  ggplot(aes(x = OR, y = reorder(city_state, OR)))+
  geom_point()+
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high))+
  labs(
    title = "Adjusted OR and CI for Solving Homicides Comparing Victims Gender",
    x = "Odds Ratio",
    y = "City_State"
  )

homicide_plot
```


###Problem 3
```{r}
#load packages
library(modelr)
library(mgcv)
```

```{r}
#load data
birthwt = read_csv("data/birthweight.csv") %>% 
  janitor::clean_names()
```
Interested in investigating the relationship between mother's pre-pregnancy weight (ppwt) and baby's birth weight because mother's pre-pregnancy weight could be an indicator of mothers' health condition and this may affect their newborns weight.

```{r}
birthwt %>% 
  ggplot(aes(x = ppwt, y = bwt)) +
  geom_point(alpha = .5) #plot the trend between ppwt and bwt
```
From the graph we can see that there is not a clear linear relationship between ppwt and bwt. But let's try fit a simple linear regression between mother's pre-pregnancy weight and baby's birth weight anyways.

```{r}
#fit a SLR model
linear_mod = lm(bwt ~ ppwt, data = birthwt)
linear_mod %>% 
  broom::tidy()
```

```{r}
birthwt_plot = birthwt %>% 
  modelr::add_residuals(linear_mod) %>% #add residuals
  modelr::add_predictions(linear_mod) %>% #add predictions
  ggplot(aes(x = pred, y = resid))+
  geom_point()+
  geom_smooth(se = F, method = "lm")

birthwt_plot #plot residuals against fitted values
```
The plot does not has a random pattern and evenly distributed around 0, which may indicate the model does not meet homoscedasticity.

```{r}
#run MLR model with length at birth and gestational age
mlr_mod = lm(bwt ~ blength + gaweeks, data = birthwt) 
summary(mlr_mod)

#run MLR model with head circumference, length, sex and their interactions
inter_mod = lm(bwt ~ bhead*blength*babysex, data = birthwt)
summary(inter_mod)
```

```{r}
#cross validation between models
cv_df =
  crossv_mc(birthwt, 1000) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
#get corresponding RMSEs for the testing data 
cv_df = 
  cv_df %>% 
  mutate(
    linear_mod  = map(train, ~lm(bwt ~ ppwt, data = .x)),
    mlr_mod     = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    inter_mod   = map(train, ~lm(bwt ~ bhead*blength*babysex, data = as_tibble(.x)))) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_mlr    = map2_dbl(mlr_mod, test, ~rmse(model = .x, data = .y)),
    rmse_inter  = map2_dbl(inter_mod, test, ~rmse(model = .x, data = .y)))
```

```{r}
#plot the prediction error distribution for each candidate model
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
From the graph, we can clearly see that the RMSEs for linear model are significantly higher than the MLR model and Interaction model. Therefore, fitting ppwt and bwt with a simple linear model is definately not ideal. Between MLR model and Interaction model, the latter one has lower rmse. Therefore, baby's head circumference, length, and sex are interacting with each other and the Interaction model is better than the MLR model with length at birth and gestational age as predictors.
